Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\subsection{Performance Regression Detection in DevOps}
This study \cite{regression-detection} proposes to perform regression detection performance at the DevOps stage, i.e. at the level of the source code change. The main thing considered is to avoid detecting performance regressions after the app is deployed and running in a production environment. There are two ways proposed by the research
to detect performance regressions at the DevOps stage:
\begin{enumerate}
	\item Perform regression detection at the source code level by extracting
	every Git commit and identify which test cases are affected by
	regression on each commit. After that, the performance of each commit will be
	evaluated chronologically using the relevant test cases or
	benchmarks of performance. Finally, a statistical analysis will be carried out on the performance evaluation
	to identify which changes resulted in the performance regression. To find out the root of the problem at the code level, an iterative approach will be done  to identify the root causes of
	regression until it can no longer generate new reasons.
	\item Predict which tests may manifest regression at the commit level. This approach is a continuation of the previous point where
	the approach of doing a test on every commit takes a lot
	resources and effort so that this approach will make predictions
	automatically whether a test will manifest a performance regression given a commit code. In detail, this approach will detect whether there is a regression on certain tests of a commit. To make a prediction model, it must first be identified which tests are prone to yielding
	regression by evaluating all the tests affected by the code change in
	previous commits by calculating the performance of each test, such as response time,
	CPU and Memory usage, I/O reads and writes, by doing
	each test sequentially.
\end{enumerate}

>>>>

\subsection{Performance Regression Detection in DevOps}
This study \cite{regression-detection} proposes to perform regression detection performance at the DevOps stage, i.e. at the level of the source code change. The main thing considered is to avoid detecting performance regressions after the app is deployed and running in a production environment. There are two ways proposed by the research
to detect performance regressions at the DevOps stage:
\begin{enumerate}
	\item Perform regression detection at the source code level by extracting
	every Git commit and identify which test cases are affected by
	regression on each commit. After that, the performance of each commit will be
	evaluated chronologically using the relevant test cases or
	benchmarks of performance. Finally, a statistical analysis will be carried out on the performance evaluation
	to identify which changes resulted in the performance regression. To find out the root of the problem at the code level, an iterative approach will be done  to identify the root causes of
	regression until it can no longer generate new reasons.
	\item Predict which tests may manifest regression at the commit level. This approach is a continuation of the previous point where
	the approach of doing a test on every commit takes a lot
	resources and effort so that this approach will make predictions
	automatically whether a test will manifest a performance regression given a commit code. In detail, this approach will detect whether there is a regression on certain tests of a commit. To make a prediction model, it must first identified which tests are prone to yielding regression by evaluating all the tests affected by the code changes in previous commits by calculating the performance of each test, such as response time,
	CPU and Memory usage, I/O reads and writes, by doing
	each test sequentially.
\end{enumerate}
